Zaca Fire Type Conversion

### 2020-08-03 Model Data Sheets and Code/Manuscript_Code.Rmd
Landsat pre-processing

>>>>

## Prepare Imagery Data

### Load Function to Pre-process Landsat

The Landsat pre-processing function is stored in a separate file. For each image, it stacks the Landsat bands into a single image file. It then masks erroneous reflectance retrievals, masks clouds, and saves the new image. The function automatically iterates over every data set in a subdirectory.

source("preprocessLandsat.R")

### Pre-process Landsat Images

preprocessLandsat("E:/zaca/type_conversion/Imagery")
